Word Sense Disambiguation: Pipelining with Supervised LSA

### 2014-05-11 paper.tex
everyone on same page

	\subsubsection{Probabilistic LSA}: 
	Formulated as early as 1999 in a paper by Hofmann [CITATION], this approach is based on mixture decomposition from latent class model. It uses a probabilistic model known as an aspect model, which is a latent variable model for co-occurrence data. It introduces a conditional dependence assumption, namely that the document random variable and the word random variable are independent conditioned on the state of the associated latent variable.

@@

	\section{Algorithms}
	 Part of speech tagging and bigram models
 	 Use for subset of data that has high predictability
 	 Supervised LSA for the rest of the data

 	 Other methods had low accuracy 
 	\subsection{Part-of-Speech}
 	\subsection{Semantic Knowledge base}
        We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of $ < 30\%$, so we discarded them from the pipeline.

@@

        11. Liling Tan. 2014. Pywsd: Python Implementations of Word Sense Disambiguation (WSD) Technologies [software]. Retrieved from https://github.com/alvations/pywsd

>>>>

	\subsubsection{Probabilistic LSA}
	Formulated as early as 1999 in a paper by Hofmann [CITATION], this approach is based on mixture decomposition from latent class model. It uses a probabilistic model known as an aspect model, which is a latent variable model for co-occurrence data. It introduces a conditional dependence assumption, namely that the document random variable and the word random variable are independent conditioned on the state of the associated latent variable.

@@

	\section{Algorithms}

	 We implemented a pipeline each with a different type of algorithm in order to do 
	 word sense disambiguation. The first step is a part-of-speech tagging step that uses
	 bigram models in order to determine what the usual part of speech is in a certain location. 
	 We use this approach for a subset of data that has high predictability.

	 Previously, we had a step involving semantic knowledge approaches, but this had low accuracy and we discarded it from the pipeline. We still detail the methods below.

 	 For the rest of the data, we applied supervised LSA, a novel implementation of the simple LSA algorithm with some ideas drawn from more sophisticated LSA approaches.

 	 We detail them in the following sections.  
 	\subsection{Part-of-Speech}
 	\subsection{Semantic Knowledge base}
        We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of $ < 30\%$, so we discarded them from the pipeline.

@@

    11. Liling Tan. 2014. Pywsd: Python Implementations of Word Sense Disambiguation (WSD) Technologies [software]. Retrieved from https://github.com/alvations/pywsd.
